Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-27 LatexNotes/Notes.tex
NM

The KdV equation in dimensional form is
\begin{equation}
2 \eta_t + \frac{3 c}{h_0} \eta \eta_{\xi} + \frac{c h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Here, $\eta$ has units of length, $t$ time, $c = \sqrt{g h_0}$ is the wave speed, and $\xi = x - ct$. I obtained this equation by starting from Johnson's dimensionless equation (3.28) on page 208 and working backwards to untangle the scales that he had used to non-dimensionalize.

>>>>

The KdV equation in dimensional form is
\begin{equation}
2 \eta_t + \frac{3 c}{h_0} \eta \eta_{\xi} + \frac{c h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Here, $\eta$ has units of length, $t$ time, $h_0$ is the depth, $c = \sqrt{g h_0}$ is the wave speed, and $\xi = x - ct$. I obtained this equation by starting from Johnson's dimensionless equation (3.28) on page 208 and working backwards to untangle the scales that he had used to non-dimensionalize.
Alternatively, when the first term is expressed as a spatial derivative, the dimensional KdV equation is
\begin{equation}
2 \eta_x + \frac{3}{h_0} \eta \eta_{\xi} + \frac{h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Notice the only difference is the absence of the wavespeed $c$ and the first term is now a spatial derivative.

The important thing to remember is that Johnson uses these characteristic scales for non-dimensionalizing (characteristic scales denoted by a *)
\begin{align}
\eta^* = \eps h_0 , \quad
x^* = \eps^{-1/2} h_0 , \quad
t^* = \eps^{-1/2} h_0/c
\end{align}
where $h_0$ is a characteristic depth (say the upstream depth), $c = \sqrt{g h_0}$ the corresponding wave speed, and $\eps = a / h_0$ is the ratio of wave amplitude to depth. Roughly speaking, we want to alter Johnson's non-dimensionalization so that $x$ is scaled on some characteristic wavelength (and $t$ scaled accordingly). Importantly, we need to account for variable depth.
